\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}

% Manual margins
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\topmargin}{-0.5in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}

\begin{document}

\begin{center}
    {\LARGE \textbf{NS Learn-Earn: The Economic Engine}} \\ [0.5em]
    {\Large Matching Talent to Opportunities at the Speed of the Internet} \\ [1em]
    \textbf{Adam Tomas} (Longtermer \#2) \\
    \today
\end{center}

\hrule
\vspace{1.5em}

\noindent \textbf{\large 1. THE PROBLEM: THE 40/100 MDEC GAP}
\vspace{0.5em}

\noindent \textbf{Status:} We currently have only $\sim$40 approvals. We need 60 more before the KL expansion.

\begin{itemize}
    \item \textbf{The Bottleneck:} As identified by Althea, the primary blocker is \textbf{Proof of Income}.
    \item \textbf{The Waste:} Over \textbf{\$1M in tasks} are currently sitting idle across portfolio companies because no routing system exists.
    \item \textbf{The Consequence:} Without a clear path to earn, high-potential talent is leaving.
\end{itemize}
\vspace{1em}

\noindent \textbf{\large 2. THE SOLUTION: INTERNAL ECONOMIC ENGINE}
\vspace{0.5em}

\noindent We must build the routing infrastructure that connects NS residents with portfolio company opportunities immediately.

\begin{center}
TASKS (\$50-\$500) $\rightarrow$ PAID INTERNSHIPS (\$2k/mo) $\rightarrow$ JOBS (\$4k+/mo)
\end{center}

\noindent \textbf{Goal:} Learn what pays. Earn while learning. Get MDEC qualified.

\vspace{1em}
\noindent \textbf{Shipped Infrastructure (Proof of Work)} \\
I have already built the initial components of this engine:
\begin{itemize}
    \item \textbf{SkillMarketCap.com:} Real-time skill pricing data visualization.
    \item \textbf{Launch Strategy:} Ghost-drafted the "Earn" launch post to unblock the \$1M task flow.
    \item \textbf{Internal Tools:} Deployed \texttt{ns-tutorial-generator} and \texttt{ns-issue-estimator}.
    \item \textbf{Traction:} 4 tasks submitted, 2 Learn-Luma events hosted.
\end{itemize}
\vspace{1em}

\noindent \textbf{\large 3. SUCCESS METRICS (90 DAYS)}
\vspace{0.5em}

\begin{itemize}
    \item \textbf{10+} residents matched \& earning through tasks.
    \item \textbf{5+} residents MDEC-qualified via the \$2k/mo threshold.
    \item \textbf{5+} portfolio companies hiring actively through the system.
    \item \textbf{Replicable Playbook:} A system ready for every future cohort.
\end{itemize}
\vspace{1em}

\noindent \textbf{\large 4. WHY ME? (LONGTERMER \#2)}
\vspace{0.5em}

\begin{enumerate}
    \item \textbf{Living the Problem:} I am a resident who needs the MDEC visa. My incentives are perfectly aligned with the user base.
    \item \textbf{Bootcamp Native:} As an App Academy grad, I intimately understand the "train-to-hire" model.
    \item \textbf{Committed:} 8+ months of commitment to the Network School vision.
\end{enumerate}
\vspace{1em}

\noindent \textbf{\large 5. THE ASK: 1-3 MONTH TRIAL}
\vspace{0.5em}

\noindent \textbf{Proposal:} A 3-month trial period to formalize the Economic Engine role.

\begin{itemize}
    \item \textbf{Rate:} \$2,000 / month (Standard MDEC Qualification Rate).
    \item \textbf{Format:} Cash (for MDEC proof) + NS Points (Long term upside).
    \item \textbf{Start Date:} Immediate.
\end{itemize}

\noindent \textit{If it works, we formalize. If not, no hard feelings. Low risk, high upside.}

\vspace{2em}
\hrule
\vspace{0.5em}
\begin{center}
    \textbf{Adam Tomas} | adamtomas.fun | github.com/adamtomaspang
\end{center}

\end{document}
