\documentclass[11pt]{article}

% Minimal packages only
\usepackage[utf8]{inputenc}

% Manual margins since geometry might be missing
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\topmargin}{-0.5in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}

\begin{document}

\begin{center}
    {\LARGE \textbf{Adam Pangelinan}} \\ [0.5em]
    Network School, Singapore-Johor SEZ, Malaysia \\
    adamtpangelinan@gmail.com | 1-671-686-2020 \\
    github.com/adamtomaspang | @adamtomaspang | \textbf{adamtomas.fun}
\end{center}

\hrule
\vspace{1em}

\noindent \textbf{\large SUMMARY}
\vspace{0.5em}

\noindent Execution-first Software Engineer and "Longtermer \#2" at the Network School. Currently building the \textbf{Learn-Earn Economic Engine} to solve the MDEC residency bottleneck. Proficient in rapidly shipping production apps using React, Python/Django, and AI-assisted workflows. Seeking to formalize Core Team role to scale the school's digital infrastructure.
\vspace{1.5em}

\noindent \textbf{\large NETWORK SCHOOL PROJECTS (CURRENT)}
\vspace{0.5em}

\noindent \textbf{The Learn-Earn Engine} \hfill Oct 2024 -- Present \\
\textit{Lead Architect \& Developer} \hfill Network School
\begin{itemize}
    \item \textbf{MDEC Residency Solution:} Designed and currently building the routing infrastructure to connect \$1M+ in idle portfolio company tasks to residents, directly addressing the visa income requirement.
    \item \textbf{SkillMarketCap.com:} Shipped a real-time data visualization tool for tracking resident skill value, demonstrating complex API consumption and React state management.
    \item \textbf{NS Internal Tools:} Developed \textit{NS Issue Estimator} and \textit{Tutorial Generator} to streamline community contributions, aligning with the JD's "Internal Tools" requirement.
    \item \textbf{Physical Infrastructure:} Established the physical "Classroom" node to facilitate deep work and co-learning sessions.
\end{itemize}
\vspace{1em}

\noindent \textbf{\large TECHNICAL SKILLS}
\vspace{0.5em}

\noindent \textbf{Languages:} JavaScript (ES6+), TypeScript, Python, SQL, HTML5, CSS3 \\
\noindent \textbf{Frontend:} React.js, Next.js, Redux, Tailwind CSS, Material UI \\
\noindent \textbf{Backend:} Node.js, Express, Django (Adapter), Flask, PostgreSQL, MongoDB, AWS (EC2, S3) \\
\noindent \textbf{DevOps/Tools:} Docker, Git, Nginx, Vercel, Cursor (AI Workflow), Linux/Bash
\vspace{1.5em}

\noindent \textbf{\large PROFESSIONAL EXPERIENCE}
\vspace{0.5em}

\noindent \textbf{Hilton Guam Resort \& Spa} \hfill Apr 2024 -- May 2024 \\
\textit{Software Engineer} \hfill Guam
\begin{itemize}
    \item Engineered a secure Gym Class Management Admin Panel using \textbf{Node.js}, enabling real-time schedule updates.
    \item Built a responsive guest enrollment landing page using \textbf{React.js}, optimizing UX for mobile users.
\end{itemize}
\vspace{1em}

\noindent \textbf{Blue Guam} \hfill Oct 2023 -- Nov 2023 \\
\textit{Software Engineer} \hfill Remote
\begin{itemize}
    \item Deployed secure production infrastructure for a 5-person agile team. Configured \textbf{Nginx} and Certbot for HTTPS.
    \item Containerized the full-stack application using \textbf{Docker}, hosting 4 orchestrated containers on AWS.
\end{itemize}
\vspace{1.5em}

\noindent \textbf{\large SELECTED ENGINEERING PROJECTS}
\vspace{0.5em}

\noindent \textbf{Audioboogie} \hfill Oct 2023 \\
\textit{Python, Machine Learning, Facebook TTS}
\begin{itemize}
    \item Built an automated audiobook generator using the \textbf{PyPDF2} library to parse 100k+ characters from PDF text.
    \item Integrated Facebook's TTS ML model to synthesize realistic speech, optimizing performance to run 2x faster on GPU.
\end{itemize}
\vspace{1em}

\noindent \textbf{Peeramid} \hfill Mar 2023 \\
\textit{React, Redux, Express, MongoDB}
\begin{itemize}
    \item Developed a full-stack wellness tracking application. Architected the Redux state management for 4 key user flows.
    \item Designed RESTful API endpoints in Express to handle complex data retrieval across 44 distinct routes.
\end{itemize}
\vspace{1.5em}

\noindent \textbf{\large EDUCATION}
\vspace{0.5em}

\noindent \textbf{App Academy} \hfill Nov 2022 -- Mar 2023 \\
\textit{Full Stack Web Development Immersive} \hfill Remote
\begin{itemize}
    \item 1000+ hour immersive curriculum focused on Ruby on Rails, JavaScript, and React.
\end{itemize}

\end{document}
